Looking for CDI Bias: WG Comprehension

### 2021-07-16 02-preliminary-WGcomp.Rmd
plotting high vs. low-SES DIF

#mg2s <- summary(mg2)
#fem = mg2s[[1]]$rotF
#mal = mg2s[[2]]$rotF
big_dif %>% arrange(desc(d_diff_abs)) %>% kable(digits = 2)
```

@@

>>>>

#mg2s <- summary(mg2)
#fem = mg2s[[1]]$rotF
#mal = mg2s[[2]]$rotF
big_dif %>% relocate(definition) %>%
  arrange(desc(d_diff_abs)) %>% kable(digits = 2, format = "html", table.attr = "style='width:40%;'")
```

@@

```{r}
load(here("data/eng_wg_comp_SES_DIF.Rds"))

extract_ses_group_df <- function(group_model) {
  Mit = as_tibble(coef(group_model, simplify=T)$high$items) %>%
    mutate(definition = rownames(coef(group_model, simplify=T)$high$items)) %>%
    select(-g, -u) %>% 
    rename(d_hi = d)
  Fit = as_tibble(coef(group_model, simplify=T)$low$items) %>%
    mutate(definition = rownames(coef(group_model, simplify=T)$low$items)) %>%
    select(-g, -u) %>%
    rename(d_lo = d)

  combo <- Mit %>% left_join(Fit) %>%
    mutate(d_diff = d_hi - d_lo,
           d_diff_abs = abs(d_diff)) 
  return(combo)
}

mg2_df = extract_ses_group_df(mg2)
```

### Items with a large difference in difficulty across SES

#mg2s <- summary(mg2)
big_dif %>% relocate(definition) %>% 
  arrange(desc(d_diff_abs)) %>% kable(digits = 2, format = "html", table.attr = "style='width:40%;'")
```

### Plot item ease for high vs. low SES

```{r, fig.width=8, fig.height=6}
ggplot(mg2_df, 
       aes(x = d_lo, y = d_hi)) + 
  geom_point(alpha=.7) + 
  ggrepel::geom_label_repel(data = filter(mg2_df, d_diff_abs > thresh), 
                            aes(label = definition), max.overlaps = 20) + theme_bw() +
  xlab("Item Ease for low-SES") + 
  ylab("Item Ease for high-SES") + 
  geom_abline(intercept=0, slope=1, linetype='dashed')
```
